---
title: "R Notebook to accompany Fink, Alexander, Janata (2022)"
output: html_notebook
author: Lauren Fink
contact: lkfink@ucdavis.edu or lauren.fink@ae.mpg.de
---

This notebook steps through the mixed modelling analyses reported in the Individual Differences section of the paper. To recreate, please set the file path to the data file appropriately.

```{r, verbose=FALSE}
# Load packages and data
library(lme4)
library(nlme)
library(lmerTest)
library(car)
library(sjPlot)
library(r2glmm)
library(sjmisc)
library(sjlabelled)
library(effsize)
library(ggplot2)
library(nortest)
library(dplyr)
library(tidyverse)
library(readxl)
library(nortest)
library(PerformanceAnalytics)
library(MuMIn)
library(caret)
library(magick)
library(PEIP)
library(gplots)
library(ggeffects)

# Load our data file
# USER TODO: Set path appropriately
gd = read.csv(file = '/Users/lauren.fink/Documents/Projects/GEM/Data/four_all_wAllIndDiffs_long.csv', header=TRUE)

# recode some variables 
gd$exp = as.factor(gd$exp)
gd$gender = as.factor(gd$gender)
gd$sd_abs = abs(gd$sdDiff)
```


# Relationship between person-level variables and individual-group sd async
This is Table 4 in the paper
```{r}
lr <- lmer(sdDiff ~  gen_soph + intern + powo + chance + play + seek + care + fear + anger + sadness + (1|alpha:subID:group:exp),  
            data=gd,
            na.action=na.exclude,
            REML = TRUE)

summary(lr)

print(car::vif(lr))
```


Pretty table output for paper
```{r}
# check if overparameterized 
print(rePCA(lr)) #not overparameterized


# Do F test for model
print(Anova(lr))

# Output table with fixed and random effect results
sjPlot::tab_model(lr, 
                  show.re.var= TRUE) 
```


```{r}
preds = ggpredict(lr, terms = "sadness")
print(preds)
p = plot(preds)
p
```



# Relationship between sd and groove
Table 5. Individual groove ratings as a function of SD asynchrony difference from group
Fig. 7
```{r}
lr <- lmer(groove ~ sdDiff + (1|alpha:subID:group:exp), 
            data=gd,
            #family=binomial(link="identity"),
            na.action=na.exclude,
            REML = TRUE)

summary(lr)

```

```{r}
plot_model(lr, type = "eff", term = "sdDiff")
```

```{r}
# check if overparameterized 
print(rePCA(lr)) #not overparameterized


# Do F test for model
print(Anova(lr))

# Output table with fixed and random effect results
sjPlot::tab_model(lr, 
                  show.re.var= TRUE) 
```



# Relationship between personal rank and sd async difference
Table 6 & Figure 8

```{r}
gd$rank_factor = as.factor(gd$rank)
lr <- lmer(sdDiff ~  rank_factor + (1|alpha:subID:group:exp), 
            data=gd,
            na.action=na.exclude,
            REML = TRUE)

summary(lr)
```

```{r}
sjPlot::tab_model(lr, 
                  show.re.var= TRUE) 

preds = ggpredict(lr, terms = "rank_factor")
print(preds)
op = TRUE
if (op){png("gem_sdDiff_rank.png", units="in", width=7, height=6, res=300)}
p = plot(preds)
p + theme_classic() + xlab("Rank") + ylab("Individual - Group SD async") + theme(
      text = element_text(size=16, color="black"))
```
